\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{Grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{lipsum}
\usepackage{multicol}
\usepackage[scale=0.85]{geometry} % Reduce document margins

% ----------------------------------------------------------------------------
%		Contact Info
% ----------------------------------------------------------------------------

\firstname{David} % Your first name
\familyname{Clegg} % Your last name
\title{Curriculum Vitae}
\address{9 Cherrywood Garden}{High Wycombe, Bucks HP10 9AX}
\mobile{(+44) 7540 374 535}
\email{davidclegg95@gmail.com}

\begin {document}

\makecvtitle

\section{Computer Skills}
\begin{multicols}{3}
	Proficient in:
	\begin{itemize}
		\item{Java} 
		\item{HTML -- accessibillity experience}
		\item{CSS} 
		\item{Javascript}
		\item{XML}
	\end{itemize}
\columnbreak
	Conversant with:
	\begin{itemize}
		\item{Haskell}
		\item{Python}
	\end{itemize}
\columnbreak
	Familiar Software Packages:
	\begin{itemize}
		\item{Microsoft Office Suite}
		\item{Git}
		\item{Subversion}
		\item{Eclipse}
	\end{itemize}
\end{multicols}

\section{Academic Qualifications}
\cventry{}{1st Year at Birmingham University studying  Computer Science}{}{}{}
{Achieved a first in first year with an overall mark of \textbf{80\%} including:
\begin{itemize}
	\item \textbf{84\%} in Software Workshop (Java programming)
	\item \textbf{86\%} in Foundations of Computer Science (functional programming and data structures)
	\item \textbf{85\%} in Robot Programming
\end{itemize}
}

\cventry{}{A levels}{}{A grade in Maths and Physics, B grade in Further Maths}{}
{}
\cventry{}{GCSEs}{}{8 A* grades, 2 A grades, 3 B grades}{}
{}

\section{Work Experience}

\cventry{July 2014 -- August 2014 }{Private consultant on ChemAccess project for one of my lecturers}{ }{}{}{
Completely redesigned the ChemAccess website and then wrote the classes which identified functional groups in chemical equations. The system was designed to make chemical diagrams written in textbooks more accessible to visually impared students. My classes were used to assist the parsing of the molecule so it could be more intuitively presented.
}

\cventry{July 2013}{IT Assistant at John Hampden Grammar School}{ }{}{}{
In charge of installing the computer suite in the new school library, Installed software on the computers and connected them to the network.
}

\cventry{Sept 2011 -- Current}{Tutor at Explore Learning}{}{}{}{
Successfully delivered the flagship maths workshop, 
Communicated the children's academic progress to their parents,
Tutored children in Maths and English.
}


\section{Other relevant Experience}

\cventry{Oct 2014}{Represented the University of Birmingham in the CISCO hackathon }{}{}{}{
	Worked as a team to rapidly prototype a solution to a technology problem in a 24 hour hackathon. Our task was to create an innovative application to improve the safety of railways which we then presented to CISCO executives
}

\cventry{Sept 2014}{Part of the team that represented the UK in the international stages of the Capgemini Supertechies show}{}{}{}{
	Presented a solution to a business and technology challenge to a panel of experts and then recorded a short and concise version to be broadcast on Indian TV.
}

\cventry{July 2014}{Negotiated a 40\% discount with a kit supplier in my role on the committee of the Muay Thai society}{}{}{}{
	As the public relations and kit representative of the Muay Thai society I negotiated a deal with the UK supplier of Sandee equipment which gave the society and all affiliated clubs in the UK a 40\% discount which has saved our individual club over £1200.
}

\cventry{March 2013}{Managed a team of 25 people at the UK finals of the NASA engineering competition}{}{}{}{
	I was the project managing the team in charge of designing the automation of a space station intended to orbit the moon and allow space travel further into the solar system.
}

\cventry{Sept 2013}{Recipient of GE Star award}{}{}{}{}


\section{Key Skills}

\cventry{}{Confident communication}{}{}{}
{\begin{itemize}
	\item Condensed a detailed 25 minute presentation into a 4 minute elevator pitch to be broadcast on Indian television for the Capgemini Supertechies show.
	\item Delivered progress reports quickly and concisely to parents when working at Explore learning.
	\item Received full marks for my presentation as part of the ``Information and the web'' module in my degree.
	\item Was the public face at school events as part of the hospitality team.
\end{itemize}	
}

\cventry{}{Strong team working skills}{}{}{}
{\begin{itemize}
	\item Managed conflicts, co-operated with other team leaders and enforced deadlines in my role as a project manager at the NASA engineering competition.
	\item Worked closely with team senior management and other team members to make sure events ran smoothly while on the school hospitality team.
\end{itemize}
}

\cventry{}{Highly Motivated}{}{}{}
{
\begin{itemize}
	\item I take the initiative .
	\item Successfully worked to tight deadlines at the CISCO hackathon.
	\item Reached national stage of NASA engineering competition.
	\item Take part in lots of extra curricular competitions.
	\item Consistently high academic achievement.
\end{itemize}
}

\end{document}