\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{lipsum}
\usepackage{multicol}
\usepackage[scale=0.85]{geometry} % Reduce document margins

% ----------------------------------------------------------------------------
%		Contact Info
% ----------------------------------------------------------------------------

\firstname{David} % Your first name
\familyname{Clegg} % Your last name
\title{Curriculum Vitae}
\address{9 Cherrywood Garden}{High Wycombe, Bucks HP10 9AX}
\mobile{(+44) 7540 374 535}
\email{davidclegg95@gmail.com}

\begin {document}

\makecvtitle
\section{Academic Qualifications}
\cventry{2013 -- 2017}{Final Year BSC Computer Science student at the University of Birmingham predicted a first class degree overall}{}{}{}{}

\cventry{}{First Year:}{}{}{}{
Achieved a first in first year with an overall mark of \textbf{80\%} including:
\begin{itemize}
	\item \textbf{84\%} in Software Workshop (Java programming)
	\item \textbf{86\%} in Foundations of Computer Science (functional programming and data structures)
	\item \textbf{85\%} in Robot Programming
\end{itemize}
}

\cventry{Sept 2014 -- July 2015}{Second Year:}{}{}{}{
Achieved a first in second year with an overal mark of \textbf{76\%} including
\begin{itemize}
	\item \textbf{96\%} in Functional Programming 
	\item \textbf{88\%} in Computer Systems and Architecture 
	\item \textbf{84\%} in Team Project
\end{itemize}
}
\subsection{Secondary School Qualifications}

\cventry{Sept 2012 -- July 2013}{A levels}{}{A grade in Maths and Physics, B grade in Further Maths}{}
{}
\cventry{Sept 2009 -- July 2011}{GCSEs}{}{8 A* grades, 2 A grades, 3 B grades}{}
{}
\section{Technical Skills}

\begin{multicols}{3}
	Strong with:
	\begin{itemize}
		\item{Java} 
		\item{HTML -- accessibillity experience}
		\item{CSS} 
		\item{Javascript}
		\item{XML}
		\item{SQL}
	\end{itemize}
\columnbreak
	Proficient with:
	\begin{itemize}
		\item{Haskell}
		\item{Python}
	\end{itemize}
\columnbreak
	Familiar Software Packages:
	\begin{itemize}
		\item{Microsoft Office Suite}
		\item{Git}
		\item{Subversion}
		\item{Eclipse}
	\end{itemize}
\end{multicols}



\section{Work Experience}
 
\cventry{July 2014 -- August 2014 }{Student Intern on ChemAccess project for two of my lecturers}{ }{}{}{
Completely redesigned the ChemAccess website and then wrote the classes which identified functional groups in chemical equations. The system was designed to make chemical diagrams written in textbooks more accessible to visually impaired students. My classes were used to assist the parsing of the molecule so it could be more intuitively presented. I had  to quickly get to grips with a large existing codebase and follow the existing code's conventions to ensure readability.
}

\cventry{July 2013}{IT Assistant at John Hampden Grammar School}{ }{}{}{
	Employed by my Secondary School to help install the computer suite in the new school library. I installed software on the computers and connected them to the network. I also had to supervise students moving books and furniture to the new Library 
}

\cventry{Sept 2011 -- Current}{Tutor at Explore Learning}{}{}{}{
	As a tutor I had to deliver detailed feedback quickly and concisely to parents at the end of each session. On top of my normal responsibilities as a tutor I successfully planned and delivered the lessons for the flagship maths workshop ``Creative Maths''. 
}


\section{Other relevant Experience}

\cventry{Oct 2014}{Represented the University of Birmingham in the CISCO hackathon }{}{}{}{
	Worked as a team to rapidly prototype a solution to a technology problem in a 24 hour hackathon. Our task was to create an innovative application to improve the safety of railways which we then presented to CISCO executives.
}

\cventry{Sept 2014}{Reached the international semi-finals of the Capgemini Supertechies competition}{}{}{}{
	My team and I were flown to India to present our solution to a business and technology challenge to a executives from Capgemini and Tata power. We had to produce a detailed 25 minute presentation to be given to the panel and then a concise 4 minute version to be televised.
}

\cventry{July 2014}{Public Relations Representative for the Muay Thai society}{}{}{}{
	As the public relations and kit representative of the Muay Thai society I negotiated a deal with the UK supplier of Sandee equipment which gave the society and all affiliated clubs in the UK a 40\% discount which has saved our individual club over \pounds{1200}.
}

\cventry{March 2013}{Managed a team of 12 people at the UK finals of the NASA engineering competition hosted at Imperial College London}{}{}{}{
	I was the project managing the sub-team in charge of designing the automation of a space station intended to orbit the moon and allow space travel further into the solar system. In my role I had to Manage Conflicts with other sub-teams and make sure my team hit the deadlines we had been given. I had to then deliver a presentation on the section I had worked on to a panel of NASA engineers and 100 other students.
}
\cventry{Nov 2011 - April 2014}{A member of the hospitality team at my old school known as the ``Men in black''}{}{}{}
{In this role I was front of house at most of the school's public events as well as coordinating with the senior management to make sure events ran smoothly.}

\cventry{Sept 2013}{Recipient of GE Star award}{}{I was the recipient of the GE Star award against international competition}{}{}

\section{references}
\cventry{Referee 1:}{Mark Lee}{m.g.lee@cs.bham.ac.uk}{Lecturer and Employer}{}{}
\cventry{Referee 2:}{Andy Wright}{Assistant Head at Secondary School}{}{}{}

\section{Interests}

\cventry{}{Martial Arts}{}{}{}
{
	I have done martial arts for 9 years, starting with Taekwondo for 8 years and, since I moved to University,  Muay Thai (Thai Boxing). At the end of first year I joined the Muay Thai Committee as Public Relations and Kit rep and negotiated an important discount with a new kit retailer as our old one went out of business. 
}
\cventry{}{Trekking}{}{}{}
{
	In \textbf{2011} I went to Ukraine to work in an orphanage in Kiev and then spend 5 days trekking in Crimea. I also have been on numerous treks in the Breacon Beacons and in Snowdonia. As well the physical challenges I enjoy the logistical challenges of having to pack everything you need for a 5 day expedition on your back as it brings the interesting compromise of weight vs kit you might need.
}

\cventry{}{``Tinkering''}{}{}{}
{
	Technology has always fascinated me and I am currently working on converting a Raspberry Pi into a retro games console.
}

\end{document}